Appendix: Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-07 appendix.qmd
Added initial computation for the side length
Added intial triangle
Added notations for the triangles

>>>>

```{r}

triangle_temp <- tibble(
  x = c(0, 4, 0),
  y = c(0, 0, 3)
)

triangle_line_temp <- tibble(
  x = c(4, 0, 4),
  xend = c(0, 0, 0),
  y = c(0, 0, 0),
  yend = c(0, 3, 3)
)

triangle_arrow_temp <- tibble(
  x = c(4 + 0.04, 0 - 0.06, 4 + 0.06),
  xend = c(0 + 0.04, 0 - 0.06, 0 + 0.06),
  y = c(0 - 0.04, 0 - 0.06, 0 + 0.06),
  yend = c(0 - 0.04, 3 - 0.06, 3 + 0.06)
)

triangle_plot <- ggplot() +
  # geom_point(
  #   data = triangle_temp,
  #   aes(
  #     x = x,
  #     y = y
  #   )
  # ) +
  geom_segment(
    data = triangle_line_temp,
    aes(
      x = x,
      xend = xend,
      y = y,
      yend = yend
    )
  ) + 
  annotate("text", x=-1, y= 1.5, 
           label = expression(frac(a[2] - a[1], 2)), 
           color = "black", hjust=-0.2) + 
  annotate("text", x=1.5, y= -0.3, 
           label = expression(frac(a[1], 2)), 
           color = "black", hjust=-0.2) + 
  annotate("text", x=2.5, y= 1.5, 
           label = expression(l), 
           color = "black", hjust=-0.2)
```

```{r}
#| out-height: 30%
triangle_plot
```

By pythagorean theorem,

$$
l^2 = (\frac{a_1}{2})^2 + (\frac{a_2 - l}{2})^2
$$
$$
l^2 - (\frac{a_2 - l}{2})^2 = (\frac{a_1}{2})^2
$$
$$
[l - (\frac{a_2 - l}{2})][l + (\frac{a_2 - l}{2})] = (\frac{a_1}{2})^2
$$

$$
3l^2 + 2la_2 - (a_1^2 + a_2^2) = 0
$$

$$
l = \frac{-2a_2 \pm \sqrt{4a_2^2 - 24[-(a_1^2 + a_2^2)]}}{6}
$$
$$
l = \frac{-a_2 \pm \sqrt{a_2^2 - 6[-(a_1^2 + a_2^2)]}}{3}
$$
